Context Inconsistency Management \\in Pervasive Systems

### 2011-04-12 paper/paper.tex
extend fuzzy section

\section{From Ontology to CCT}
As stated above the Partial Constraint Checking (PCC) algorithm is much faster than Entire Constraint Checking due to the fact that a Consistency Computation Tree (CCT) is used to store the constraints belonging to a (set of) context(s). We also stated that the ontology based context model is the most promising type of model to capture context information. Although the context model appears as a tree (see Fig. \ref{fig:ont}), the PCC algorithm cannot be directly applied to it.

\begin{figure}[htb]
  \centering
  \includegraphics[width=3.5in]{Ontology.eps}
  \caption{An example of an ontology based context model Source:~\cite{bu:2006:CCM}}
  \label{fig:ont}
\end{figure}

The model is actually a part of a larger ontology, but it is sufficient for this section. Now it needs to be transformed into a CCT for PCC. With a CCT the main focus should be on the context set of a single entity in the model. The transformation itself can be done automatically with a depth-first search algorithm, but there is no such algorithm available at this time. However, we can give a few examples of the CCT based on this ontology model. The context set of the entity \textit{Student} will be focused on. Lets say that the entity \textit{Student} is located in the \textit{Place} entity \textit{Road}, then the CCT will look as the upper tree in Fig. \ref{fig:cct1}.

\begin{figure}[htb]
  \centering
  \includegraphics[width=3.5in]{smallCCT1.eps}
  \caption{The CCTs of \textit{Student}}
  \label{fig:cct1}
\end{figure}

If the system suddenly decides that \textit{Student} is located in a \textit{Lab}, then the tree will be updated to the lower tree. Note that the system can decide in a multitude of ways that \textit{Student} is located in the \textit{Lab} by for example invalidating the earlier constraint branch after a certain amount of time or by for example basing the new \textit{Place} on the information in a new context set. Also note that the leaf of a branch cannot contain an entity that is not available in the context model. So \textit{Student} cannot be located in, for example, \textit{Car}, because it is not part of the model. Even if the location in a context would be \textit{Car}, then the system would consider the location as an inconsistency in the context and detect it very quickly with PCC.

@@

\section{Fuzzy Ontologies}
In pervasive computing traditionally first order logic is used to model the environment of an application. This results in a so called ontology based context model. Every observation that does not exactly fit in this model results into a conflict. This conflict can lead to misadjusted behavior in applications unless they are timely detected and resolved~\cite{xu:2010:PCC}. Because it is impossible to perfectly model the un-predictive environment in which context-aware applications run, it would be nice if the context model was more resilient to unexpected observations. As we illustrate in the case study below, this can be obtained by using fuzzy ontologies.
\subsection{Case Study}
Suppose we want to build a context-aware application that has certain notion of teacher's activities to assist them in the best possible way (for instance automatically opening slides when a lecture starts). In the traditional approach we could build an ontology specifying where lectures take place and that a lecture starts when the teacher appears at the lectern. If now an unpredicted observation is made (sensor cross read or teacher momentarily leaves the room), an inconsistency occurs that has to be resolved for the application to proceed with normal operation. In the fuzzy ontology approach these unpredictable events can simply be modeled so that the ontology is more robust and always yields the most apt interpretation of the environment without conflict resolution. A simplified example of such an ontology is depicted in Fig.~\ref{fig:fuzzy}.
\begin{figure}[htb]
  \centering
  \includegraphics[width=3.5in]{fuzzy}
  \caption{Fuzzy ontology specifying teachers activities and their most probable location.}
  \label{fig:fuzzy}
\end{figure}
Using this fuzzy ontology the relative probability of each specified higher-level context can be calculated from the contexts in the observation window. For instance the observation sequence [$L_1$, $L_2$, $L_3$, $A_1$, $A_2$] gives a relative probability of 0.9998 for `Lecturing' and 0.0002 for `Working', event though the observations are clearly conflicting, since the teacher clearly cannot be at the lectern and in the aisle at the same time. The sequence of [$L_1$, $A_1$, $A_2$, $O_1$, $O_2$] gives a 0.941 probability for `Working' and 0.059 for `Lecturing', even though the teacher strictly spoken cannot be at the lectern and in the office at the same time (see appendix for exact calculations).

@@

Note that it is possible to extend the simple fuzzy ontology from the use case by specifying start and transition probabilities for the higher-level contexts, just as hidden Markov models\footnote{http://en.wikipedia.org/wikiHidden\_Markov\_model} do, and other information such as the expected lecture time window (fuzzified of course~\cite{Buckley1995245}).

@@

Then we have shown examples of CCTs of entities in an ontology based context model. We have not shown an algorithm on how to do this efficiently as we don't know the formal definition of OWL at this point in time. However, with the definitions of OWL one can create a depth-first search algorithm which transforms an ontology in multiple CCTs (one for each leaf entity in the model).

@@

\bibliographystyle{abbrv}
%%use following if all content of bibtex file should be shown
%\nocite{*}
\bibliography{paper}
\newpage
\appendix
\section{Fuzzy Ontology Calculations}
Observed Context Set 1: $[L_1, L_2, L_3, A_1, A_2]$
\begin{align}
                          Lecturing &= .8 * .8 * .8 * .15 * .15 * c_1\\
                                    &= .01152 * c_1\\
                                    &= 0.9998\\
                            Working &= .05 * .05 * .05 * .15 * .15 * c_1\\
                                    &= 0.000002813 * c_1\\
                                    &= 0.0002
\end{align}
Observed Context Set 2: $[L_1, A_1, A_2, O_1, O_2]$
\begin{align}
                          Lecturing &= .8 * .15 * .15 * .05 * .05 * c_2\\
                                    &= 0.000045 * c_2\\
                                    &= 0.059\\
                            Working &= .05 * .15 * .15 * .8 * .8 * c_2\\
                                    &= 0.00072 * c_2\\
                                    &= 0.941
\end{align}
\end{document}

>>>>

@@

\section{Fuzzy Ontologies}
In pervasive computing traditionally first order logic is used to model the environment of an application. This results in a so called ontology based context model. Every observation that does not exactly fit in this model results into a conflict. This conflict can lead to misadjusted behavior in applications unless it is timely detected and resolved~\cite{xu:2010:PCC}. Because it is impossible to perfectly model the unpredictable environment in which context-aware applications run, it would be nice if the context model was more resilient to unexpected observations. This resilience can be obtained by using a fuzzy ontology: a stochastic model representing lower level contexts (for instance sensory data) and their probabilities in the presence of higher level contexts (for instance user activities). The most simple approach to this would be using a hidden Markov Model\footnote{http://en.wikipedia.org/wikiHidden\_Markov\_model}: a statistical model of the environment with unobserved states (the higher level contexts) in which future states only depend on the present state. The use of such a model is illustrated in the case study below.

\subsection{Case Study}
Suppose we want to build a context-aware application that has certain notion of teacher's activities to assist them in the best possible way (for instance automatically opening slides when a lecture starts). In the traditional approach we could build an ontology specifying where lectures take place and that a lecture starts when the teacher appears at the lectern. If now an unpredicted observation is made (sensor cross read or teacher momentarily leaves the room), an inconsistency occurs that has to be resolved for the application to proceed with normal operation. In the fuzzy ontology approach these unpredictable events can simply be modeled so that the ontology is more robust and always yields the most apt interpretation of the environment without conflict resolution. A simplified example of such an ontology is depicted in Fig.~\ref{fig:fuzzy}.
\begin{figure}[htb]
  \centering
  \includegraphics[width=3.5in]{fuzzy}
  \caption{Fuzzy ontology specifying teachers activities and their most probable location.}
  \label{fig:fuzzy}
\end{figure}

Observed Context Set 1: $[L_1, L_2, L_3, A_1, A_2]$
\begin{align}
                          Lecturing &= .8 * .8 * .8 * .15 * .15 * c_1\\
                                    &= .01152 * c_1\\
                                    &= 0.9998\\
                            Working &= .05 * .05 * .05 * .15 * .15 * c_1\\
                                    &= 0.000002813 * c_1\\
                                    &= 0.0002
\end{align}
Observed Context Set 2: $[L_1, A_1, A_2, O_1, O_2]$
\begin{align}
                          Lecturing &= .8 * .15 * .15 * .05 * .05 * c_2\\
                                    &= 0.000045 * c_2\\
                                    &= 0.059\\
                            Working &= .05 * .15 * .15 * .8 * .8 * c_2\\
                                    &= 0.00072 * c_2\\
                                    &= 0.941
\end{align}

Using this fuzzy ontology the relative probability of each specified higher-level context can be calculated from the contexts in the observation window. For instance the observation sequence [$L_1$, $L_2$, $L_3$, $A_1$, $A_2$] gives a relative probability of 0.9998 for `Lecturing' and 0.0002 for `Working', event though the observations are clearly conflicting, since the teacher clearly cannot be at the lectern and in the aisle at the same time. The sequence of [$L_1$, $A_1$, $A_2$, $O_1$, $O_2$] gives a 0.941 probability for `Working' and 0.059 for `Lecturing', even though the teacher strictly spoken cannot be at the lectern and in the office at the same time (see appendix for exact calculations).

@@

Note that it is possible to extend the simple fuzzy ontology from the use case by specifying start and transition probabilities for the higher-level contexts, just as hidden Markov models do, and other information such as the expected lecture time window (fuzzified of course~\cite{Buckley1995245}).

@@

@@

\bibliographystyle{abbrv}
%%use following if all content of bibtex file should be shown
%\nocite{*}
\bibliography{paper}
\end{document}
